---
title: "Hello, Quarto"
author: "Carissa Gervasi"
format: html
editor: visual
bibliography: references.bib
---

## Quarto

This is a test document to play around with what quarto can really do. Let's say I want to play around with some of the MRIP data. First I am going to pull data from a [data query](https://www.fisheries.noaa.gov/data-tools/recreational-fisheries-statistics-queries). Let's see if we can add a hyperlink. Oh that's quite fun. OK, so we pulled data from this data query and saved it. I saved it in the My Github Projects folder on my desktop. I think it will add to Github. We will check later. OK, so we are going to do a few things here:

1.  read in the data

2.  plot the data

3.  change up the format of the output

Let's do it!

## Bringing in the code

OK, first let's bring in the file

```{r}
dat = read.csv("Data/mrip_effort_series_1981_2022_annual_GOM_allmodes_allareas.csv")
head(dat)

# remove year 2022 because preliminary
dat = subset(dat, dat$Estimate.Status == "FINAL")

```

## Plotting the data

Cool! That was step 1. Now for step 2 we want to plot the data

```{r}
#| message: false
library(tidyverse)

ggplot(dat, aes(x=Year, y=Angler.Trips)) +
  geom_point() +
  geom_line() +
  theme_classic()
```

## What else?

YAY! Wow that was fun. OK now, we want to see what this looks like in different formats. Right now we are making an html file. Where does this file get saved? It gets saved automatically in our working directory. Cool, cool. Let's push this to Github and see what happens.

Ok we got the Mendeley references in after some headache. Quarto does not seem to recognize the italics denoted in the titles. We will have to see about changing citation format. \*\*\*Spoiler alert - Mendeley is no good. Zotero is waaaaaaay better.

## What else can we do?

| Hello | Cool  | Yea |
|-------|:-----:|:---:|
| 1     |  dog  |  2  |
| 3     |  cat  |  2  |
| 87    | mouse |  3  |

I got rid of the Mendeley library. I am going to see if I can link Zotero [@gervasi2022].

HA! That was sooooo easy!!! ERMAGERD...

Next we need to figure out how to change the reference format. Ok we can do it with a csl file, but we need to download them from the website. For another day.
